---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# myGolemApp

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/mjfrigaard/shiny-app-setups/branch/main/graph/badge.svg)](https://app.codecov.io/gh/mjfrigaard/shiny-app-setups?branch=main)
<!-- badges: end -->

The goal of `myGolemApp` is to demonstrate the `golem` framework.

## Installation

You can install the development version of `myGolemApp` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mjfrigaard/shiny-app-setups")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(myGolemApp)
# myGolemApp::moviesApp()
```

## Code of Conduct

Please note that the `myGolemApp` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
